\texttt{SuperScreen}: An open-source package for simulating the magnetic response of two-dimensional superconducting devices

### 2021-10-21 main.tex
Updates from Overleaf

fig, axes = plt.subplots(2, 2, figsize=(8, 8), constrained_layout=True)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, opt_steps in zip(axes, optimesh_steps):
    title = f"optimesh_steps = {opt_steps}"
    for ax, device in zip(row, (ring, square_ring)):
        # Generate the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        # Visualize the mesh
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
        ax.axis("off")
        ax.set_title(title, fontfamily="monospace")
axes[0, 0].legend(loc="best")
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}

\begin{figure}[!h]
\centering
\begin{subfigure}{.235\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
  \caption{\inline{optimesh_steps=400}.}
  \label{fig:circular_ring_mesh}
\end{subfigure}%
\begin{subfigure}{.235\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
  \caption{\inline{optimesh_steps=None}.}
  \label{fig:circular_ring_mesh_no_opt}
\end{subfigure}%
\begin{subfigure}{.235\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
  \caption{\inline{optimesh_steps=400}.}
  \label{fig:square_ring_mesh}
\end{subfigure}
\begin{subfigure}{.235\textwidth}
  \centering
  \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
  \caption{\inline{optimesh_steps=None}.}
  \label{fig:square_ring_mesh_no_opt}
\end{subfigure}
\caption{Device geometry and mesh for a circular (a, b) and square ring (c, d) generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (a, c) and without (b, d) \inline{optimesh} optimization.}
\label{fig:ring_mesh}
\end{figure}

>>>>

fig, axes = plt.subplots(2, 2, figsize=(8, 8), facecolor="w", constrained_layout=True)
axlist = list(axes.flat)
# Create the Devices
ring = make_ring(square=False)
square_ring = make_ring(square=True)
# min_triangles specifies the minimum number of mesh elements.
min_triangles = 12000
# optimesh_steps specifies the the number of iterations of
# optimesh optimization to perform.
# Set optimesh_steps=None to disable optimesh optimization.
optimesh_steps = (None, 40)
# For more meshing options, see the docstring for Device.make_mesh().
for row, device in zip(axes, (ring, square_ring)):
    for ax, opt_steps in zip(row, optimesh_steps):
        # Generate the mesh
        device.make_mesh(min_triangles=min_triangles, optimesh_steps=opt_steps)
        # Visualize the mesh
        device.plot_mesh(ax=ax, color="gray", linewidth=0.75)
        device.plot_polygons(ax=ax, linewidth=3, legend=False)
        label = "abcd"[axlist.index(ax)]
        title = f"{label}) optimesh_steps = {opt_steps}"
        ax.set_title(title, fontsize=16, fontfamily="monospace")
        ax.axis("off")
axlist[0].legend(loc="best")
\end{minted}
\captionof{listing}{Generating and visualizing the computational mesh.}
\label{code:mesh_generation}
\end{code}

\begin{figure}[h]
    \centering
    \includegraphics[width=0.55\textwidth]{examples/images/mesh.pdf}
    \caption{Computational meshes for }
    \label{fig:mesh}
\end{figure}

% \begin{figure}[!h]
% \centering
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh.png}
%   \caption{\inline{optimesh_steps=400}.}
%   \label{fig:circular_ring_mesh}
% \end{subfigure}%
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/circular_ring_mesh_no_optimesh.png}
%   \caption{\inline{optimesh_steps=None}.}
%   \label{fig:circular_ring_mesh_no_opt}
% \end{subfigure}%
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh.png}
%   \caption{\inline{optimesh_steps=400}.}
%   \label{fig:square_ring_mesh}
% \end{subfigure}
% \begin{subfigure}{.235\textwidth}
%   \centering
%   \includegraphics[width=\linewidth]{examples/images/ring/square_ring_mesh_no_optimesh.png}
%   \caption{\inline{optimesh_steps=None}.}
%   \label{fig:square_ring_mesh_no_opt}
% \end{subfigure}
% \caption{Device geometry and mesh for a circular (a, b) and square ring (c, d) generated using Code Blocks~\ref{code:device} and \ref{code:mesh_generation}, with (a, c) and without (b, d) \inline{optimesh} optimization.}
% \label{fig:ring_mesh}
% \end{figure}
